---
title: "R Notebook"
output: html_notebook
---

Most missing data (NA) columns were valid categories. Replace with 'None'? 

```{r}
setwd("~/DataScience/MachineLearningProject/data")
library(dplyr)
df = read.csv('train.csv')

# when LotFrontage=NA, 226 are detached family homes
#df1 = df  %>% filter(is.na(LotFrontage) & (BldgType=='1Fam'))
train = df


```

Following is code to compute the correlation of all numerical columns. 

```{r}
library(corrplot)
# correlation matrix
# keep numerical columns
numericVars <- which(sapply(train, is.numeric)) #index vector numeric variables
numericVarNames <- names(numericVars) #saving names vector for use later

# correlation matrix
train_numVar <- train[, numericVars]
cor_numVar <- cor(train_numVar, use="pairwise.complete.obs") #correlations of all numeric variables

#sort on decreasing correlations with SalePrice
cor_sorted <- as.matrix(sort(cor_numVar[,'SalePrice'], decreasing = TRUE))

#select only high correlations
CorHigh <- names(which(apply(cor_sorted, 1, function(x) abs(x)>0.1)))
cor_numVar <- cor_numVar[CorHigh, CorHigh]

corrplot(cor_numVar, tl.col="black", tl.pos = "lt")
corrplot(cor_numVar, method = "ellipse")
corrplot(cor_numVar, method = "color")


```

Let's now try to order our variables in the order of the t-stats of univariate regressions. 
```{r}
numericVars = which(sapply(train, is.numeric)) #index vector numeric variables
numericVarNames = names(numericVars) #saving names vector for use later

# I eliminate some categorical numerical columns (categories coded as numbers)
# manually here. But I need to write some smarter code to eliminate them 
# automatically
numericVarNames = numericVarNames[!numericVarNames %in% 
                c("Id", "SalePrice", "OverallQual", "GarageCars", 
                  "YearBuilt", "YearRemodAdd", "GarageYrBlt", 
                  "Fireplaces", "FullBath", "MSSubClass", 
                  "HalfBath", "BsmtFullBath", "BsmtHalfBath", "KitchenAbvGr", "BedroomAbvGr", 
                  "EnclosedPorch", "ScreenPorch", "OverallCond", "TotRmsAbvGrd", 
                  "MoSold", "YrSold", "MiscVal")] 

#MiscVal and MiscFeature: value of misc feature, but this is odd: "elevator" etc. Hard to predict, eliminate it ???

nVars = length(numericVarNames)
PValExtract = function(ireg)
{
  varname = numericVarNames[ireg]
  model = lm(as.formula(paste('SalePrice ~ ', varname)), data=train)  
  coeff = coef(summary(model))
  pval = coeff[2,"Pr(>|t|)"]  
}

pvals = sapply(1:nVars, PValExtract)
bestPredictors = data.frame(name=numericVarNames,pval=pvals)
bestPredictors = bestPredictors[order(bestPredictors$pval),]

```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
